### 2014-11-13 tex/conclusion.tex
Minor fixes

Although our approach is inspired by the work in the static analysis domain, the heap representations used by those techniques do not lend themselves for use in symbolic execution since they rely on approximations, they are inflexible in what types of relations can be expressed, and they rely on rewriting of constraints.  In this work, we present a heap summary technique for symbolic execution that maintains exactness, represents arbitrary heap structures without restrictions on aliasing relationships, and supports dynamic on-the-fly initialization of heap structures. Despite this unique combination of capabilities, the summary heap technique outperforms  state-of-the-art symbolic execution techniques, and in some cases the performance gains are considerable. We believe that performance gains in symbolic execution can naturally benefit a variety of analyses based on symbolic execution, for example, verification of properties, especially those related to the heap, test case generation, program evolution techniques such as directed incremental symbolic execution~\cite{person:pldi2011}, and other back-end analyses.

>>>>

Although our approach is inspired by the work in the static analysis
domain, the heap representations used by those techniques do not lend
themselves to symbolic execution since they rely on
approximations, they are inflexible in what types of relations can be
expressed, and they rely on rewriting of constraints.  In this work,
we present a heap summary technique for symbolic execution that
maintains exactness, represents arbitrary heap structures without
restrictions on aliasing relationships, and supports dynamic
on-the-fly initialization of heap structures. This unique
combination of capabilities enables the summary heap to outperform
state-of-the-art symbolic execution techniques, and in some cases, the
performance gains are considerable. We believe that performance gains
in symbolic execution can naturally benefit a variety of analyses
based on symbolic execution, for example, verification of properties,
especially those related to the heap, test case generation, program
evolution techniques such as directed incremental symbolic
execution~\cite{person:pldi2011}, and other back-end analyses.
